rObsPack: An R package for the NOAA global observations ObsPack methane GLOBALVIEW+

### 2023-05-08 paper/paper.Rmd
paper
readme

| Function              | Description                                       |
|-----------------------|---------------------------------------------------|
| `invfile`             | Class with `print`, `summary` and `plot` methods  |
| `obs_addltime()`      | Add local time based on metadata and longitude    |
| `obs_addtime()`       | Add UTC time                                      |
| `obs_addzero()`       | Format numbers to match specific requirements     |
| `obs_agg()`           | Aggregates ObsPack by time                        |
| `obs_find_receptors()`| Find expected receptors and NetCDF files          |
| `obs_format()`        | Format for some columns of data.table             |
| `obs_freq()`          | Return numeric vector in intervals                |
| `obs_invfiles()`      | Construct `invfile` objects                       |
| `obs_list.dt()`       | Rbind list of data.frames with different names    |
| `obs_meta()`          | Reads ObsPack metadata                            |
| `obs_out()`           | Outersect, opposed as intersect                   |
| `obs_rbind()`         | Rbind data.frames with different names            |
| `obs_read()`          | Read files, and add metadata as columns           |
| `obs_read_csvy()`     | Read csvy file and prints yaml header             |
| `obs_roundtime()`     | Round seconds from "POSIXct" "POSIXt" classes     |
| `obs_summary()`       | Construct summary of ObsPack as a data.frame      |
| `obs_table()`         | Return a data.frame with summary of data          |
| `obs_trunc()`         | Trunc numbers with a desired number of decimals   |
| `obs_write()`         | Write CSVY to disk, YAML followed by tabulated    |

>>>>

| Function              | Description                                       |
|-----------------------|---------------------------------------------------|
| `invfile`             | Class with `print`, `summary` and `plot` methods  |
| `obs_addltime()`      | Add local time based on metadata and longitude    |
| `obs_addtime()`       | Add UTC time                                      |
| `obs_agg()`           | Aggregates ObsPack by time                        |
| `obs_find_receptors()`| Find expected receptors and NetCDF files          |
| `obs_format()`        | Format for some columns of data.table             |
| `obs_freq()`          | Return numeric vector in intervals                |
| `obs_invfiles()`      | Construct `invfile` objects                       |
| `obs_list.dt()`       | Rbind list of data.frames with different names    |
| `obs_meta()`          | Reads ObsPack metadata                            |
| `obs_out()`           | Outersect, opposed as intersect                   |
| `obs_rbind()`         | Rbind data.frames with different names            |
| `obs_read()`          | Read files, and add metadata as columns           |
| `obs_read_csvy()`     | Read csvy file and prints yaml header             |
| `obs_roundtime()`     | Round seconds from "POSIXct" "POSIXt" classes     |
| `obs_summary()`       | Construct summary of ObsPack as a data.frame      |
| `obs_table()`         | Return a data.frame with summary of data          |
| `obs_trunc()`         | Trunc numbers with a desired number of decimals   |
| `obs_write()`         | Write CSVY to disk, YAML followed by tabulated    |
